---
params:
    set_title: "Vim tips"
    output_dir: 'output/'
title: "`r params$set_title`"
date: "`r Sys.Date()`"
author: Lehmann
output:
    rmdformats::material:
        highlight:      kate
        self_contained: true
        code_folding:   show
        thumbnails:     true
        gallery:        true
        fig_width:      4
        fig_height:     4
        df_print:       kable
        fig_caption:    yes
---


```{r knitr_init, echo=FALSE, results="asis", cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print = "75")
opts_knit$set(width = 75)
opts_chunk$set(echo         = TRUE,
               cache        = FALSE,
               cache.lazy   = FALSE,
               prompt       = FALSE,
               tidy         = FALSE,
               message      = FALSE,
               warning      = FALSE,
               comment      = NA,
               fig.path     = 'images_output/',
               out.width    = '70%',
               fig.align    = 'center')
```

# Some tips to use R more efficiently

## How do you see the body of a function ?
In Rstudio, you can press F2 while cursor is on any function, click on a function name while holding Ctrl or Cmd, or try `View(function_name)`. In the command line you can directly type the name of the function, e.g. `saveRDS`, or type `body(saveRDS)`, or `print(saveRDS)`. However, this will work only it's the function are written in R (not a .Primitive or .C function).

## What is a S3 method ?

## How do you convert a vector to a df ?

```{r}
c <- 1:6            # vector
c
dim(c) <- c(3,2)    # df
c
```

## How to use multiple versions of R ?
Check [this paragraph](https://docs.rstudio.com/ide/server-pro/r-versions.html#using-multiple-versions-of-r-concurrently) from the Rstudio documentation.

## How to build a R package ?
Try this super nice [blog posts](https://stirlingcodingclub.github.io/SCC_R_package/notebook/Rpackage_notes.html) and [this one](http://web.mit.edu/insong/www/pdf/rpackage_instructions.pdf) aslo.
Check if package is OK: `devtools::check(document = FALSE)`. To know about building documentation, have a look at [this](http://kbroman.org/pkg_primer/pages/docs.html).

## How to call C/C++ code from R ?
Inspired from [this](https://www.r-bloggers.com/three-ways-to-call-cc-from-r/).
